---
title: "Analyzing Pilot Results"
output:
  html_document:
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Setup: load data, define variables, etc

```{r load-data-define-variables}

rm(list=ls())

source('./scripts/utils/load_all_libraries.R')

# Load an external script which contains functions for estimating either just the learning rate, or also the asymptote
source('./scripts/utils/functions_for_fitting_learning_curves.R')

# Create parameters as starting points for estimations
i_start <- 0.5
c_start <- 0.1

# Create lower and upper bound constraints on the asymptote and learning rate
c_lower <- -Inf
c_upper <- Inf
i_lower <- -Inf
i_upper <- Inf

qc_filter <- T

# Exclude borders?
exclude_border         <- T
border_dist_to_exclude <- c(1,2)

```

# Do all the calculations of all the dependent variables

```{r analyze-dependent-variables}

source('./scripts/utils/analyze_dependent_variables.R')

```

```{r order-of-conditions}

# For each participant, list the order of conditions
condition_orders <- tibble(.rows = 5)

all_ptp <- unique(session_results_all_ptp$ptp)

for (iPtp in as.vector(all_ptp)){
        iPtp
        condition_orders[iPtp] <-
                unique(
                        session_results_all_ptp$condition[
                                session_results_all_ptp$ptp==iPtp
                                ])
}

```

# Plot performance based on border

```{r border-effects-calculate}
# Calculate first session and 2nd session performances separately
# border_effects_by_session <-
#         mean_by_border_dist_rep_long %>%
#         filter(accuracy_type %in% c('correct_exact',
#                                     'correct_one_square_away')) %>%
#         mutate(border_dist = as.factor(border_dist),
#                session = as.factor(session)) %>%
#         group_by(ptp_trunk,
#                  condition,
#                  border_dist,
#                  accuracy_type,
#                  session) %>%
#         summarise(by_session_mean = mean(correct_mean, na.rm = T),
#                   by_session_sd   = sd(correct_sd, na.rm = T),
#                   n = n()) %>% 
#         ungroup() 

```



```{r border-effects-plot1, fig.width=6, fig.height=10, warning=FALSE, message=FALSE}

# fig_border_sessions <-
#         border_effects_by_session %>%
#         # filter(accuracy_type %in% c('correct_exact')) %>%
#         droplevels() %>%
#         ggplot(aes(x=session,
#                    y=by_session_mean,
#                    fill=border_dist)) +
#         
#         # Add the average across toys
#         geom_violin() +
#         # geom_boxplot(width = 0.2) +
#         stat_summary(fun = mean,
#                      color = 'black',
#                      position = position_dodge(width = 0.9)) +
#         
#         facet_grid(condition~accuracy_type) +
#         ggtitle(paste('Accuracy by border distance',sep='')) +
#         theme(legend.position = 'top') +
#         ylab('Mean accuracy') + 
#         xlab('Session') + 
#         geom_vline(xintercept = 1.5, linetype = 'dashed')
# 
# print(fig_border_sessions)

```

```{r border-effects-plot2, fig.width=12, fig.height=5, warning=FALSE, message=FALSE}

# fig_border_sessions <-
#         border_effects_by_session %>%
#         group_by(ptp_trunk,
#                  border_dist,
#                  accuracy_type,
#                  session) %>%
#         summarise(by_session_mean = mean(by_session_mean),
#                   n = n()) %>% 
#         ungroup() %>%
#         ggplot(aes(x=session,
#                    y=by_session_mean,
#                    fill=border_dist)) +
#         
#         # Add the average across toys
#         geom_violin() +
#         # geom_boxplot(width = 0.2) +
#         stat_summary(fun = mean,
#                      color = 'black',
#                      position = position_dodge(width = 0.9)) +
#         
#         facet_grid(~accuracy_type) +
#         ggtitle(paste('Averaging Across conditions too',sep='')) +
#         theme(legend.position = 'top') +
#         ylab('Mean accuracy') + 
#         xlab('Session')+ 
#         geom_vline(xintercept = 1.5, linetype = 'dashed')
# 
# print(fig_border_sessions)

```


# Scatter plots of dependent variables:

## Rough measures: last 2 reps and last 4 reps

### Island vs Neighbor:


```{r plot-rough-measures-last-two-lm-non-lm, fig.width=6, fig.height=4}

# Last 4
sum_stats_each_participant %>%
        filter(neighbor_status != 'both',
               !condition %in% c('random_locations','no_schema'),
               accuracy_type %in% c('correct_exact','correct_one_square_away')) %>%
        droplevels() %>%
        pivot_wider(id_cols = c(ptp_trunk,
                                condition,
                                accuracy_type),
                    names_from = neighbor_status,
                    values_from = last_four_mean) %>% 
        mutate(neighbor_diff = neighbor - island) %>%
        ggplot(aes(x=condition,y=neighbor_diff)) +
        geom_violin() +
        # geom_jitter(width = 0.1, alpha = 0.2) +
        geom_dotplot(binaxis='y', stackdir='center',
                     stackratio=1, dotsize=1, fill="black",
                     alpha=0.3) +        
        geom_line(aes(group=ptp_trunk,
                      color=ptp_trunk)) +
        stat_summary(fun=mean, geom="point", shape=20, size=5, 
                     color="red", fill="red") +   
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",size=1,width=0.1,color='red') +        
        facet_wrap(~accuracy_type, nrow = 1) +
        ylab('Diff') + 
        theme(legend.position = '') +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
        ggtitle('Landmark minus non-landmark, last 4') +
        geom_hline(yintercept = 0, linetype = 'dashed')

# Last 4
sum_stats_each_participant %>%
        filter(neighbor_status != 'both',
               !condition %in% c('random_locations','no_schema'),
               accuracy_type %in% c('correct_exact','correct_one_square_away')) %>%
        droplevels() %>%
        pivot_wider(id_cols = c(ptp_trunk,
                                condition,
                                accuracy_type),
                    names_from = neighbor_status,
                    values_from = log_last_four_mean) %>% 
        mutate(neighbor_diff = neighbor - island) %>%
        ggplot(aes(x=condition,y=neighbor_diff)) +
        geom_violin() +
        # geom_jitter(width = 0.1, alpha = 0.2) +
        geom_dotplot(binaxis='y', stackdir='center',
                     stackratio=1, dotsize=1, fill="black",
                     alpha=0.3) +        
        geom_line(aes(group=ptp_trunk,
                      color=ptp_trunk)) +
        stat_summary(fun=mean, geom="point", shape=20, size=5, 
                     color="red", fill="red") +   
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",size=1,width=0.1,color='red') +        
        facet_wrap(~accuracy_type, nrow = 1) +
        ylab('Diff') + 
        theme(legend.position = '') +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
        ggtitle('Landmark minus non-landmark, LOG last 4')+
        geom_hline(yintercept = 0, linetype = 'dashed')

```

## Learning rates:

### Island vs Neighbor:

First, plot the island and neighbor values on separate plots:

We see that for correct_one_square_away we get some "outlier" learning rate parameter estimates.

```{r scatter-plots-learning-rates-landmark, fig.width=8, fig.height=6}

sum_stats_each_participant %>%
        filter(neighbor_status != 'both',
               accuracy_type %in% c('correct_exact'),
               !condition %in% c('random_locations','no_schema')) %>%
        droplevels() %>%
        ggplot(aes(x=neighbor_status,
                   y=c,
                   fill=neighbor_status)) +
        geom_violin(alpha=0.5) +
        geom_boxplot(width=0.2,
                     alpha=0.2) +
        geom_point(alpha=0.2) +
        geom_line(aes(group=ptp_trunk),
                  alpha=0.2) +
        stat_summary(fun=mean, 
                     geom="point", 
                     shape=20, 
                     size=5, 
                     color="black",
                     fill="black") +         
        facet_grid(~accuracy_type+condition) +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
        ylab('Learning Rate C')

sum_stats_each_participant %>%
        filter(neighbor_status != 'both',
               accuracy_type %in% c('correct_one_square_away'),
               !condition %in% c('random_locations','no_schema')) %>%
        droplevels() %>%
        ggplot(aes(x=neighbor_status,
                   y=c,
                   fill=neighbor_status)) +
        geom_violin(alpha=0.5) +
        geom_boxplot(width=0.2,
                     alpha=0.2) +
        geom_point(alpha=0.2) +
        geom_line(aes(group=ptp_trunk),
                  alpha=0.2) +
        stat_summary(fun=mean, 
                     geom="point", 
                     shape=20, 
                     size=5, 
                     color="black",
                     fill="black") +         
        facet_grid(~accuracy_type+condition) +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
        ylab('Learning Rate C')

# Log C
sum_stats_each_participant %>%
        filter(neighbor_status != 'both',
               accuracy_type %in% c('correct_exact'),
               !condition %in% c('random_locations','no_schema')) %>%
        droplevels() %>%
        ggplot(aes(x=neighbor_status,
                   y=c_log,
                   fill=neighbor_status)) +
        geom_violin(alpha=0.5) +
        geom_boxplot(width=0.2,
                     alpha=0.2) +
        geom_point(alpha=0.2) +
        geom_line(aes(group=ptp_trunk),
                  alpha=0.2) +
        stat_summary(fun=mean, 
                     geom="point", 
                     shape=20, 
                     size=5, 
                     color="black",
                     fill="black") +         
        facet_grid(~accuracy_type+condition) +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
        ylab('Log C') +
        ggtitle('Log C')

sum_stats_each_participant %>%
        filter(neighbor_status != 'both',
               accuracy_type %in% c('correct_one_square_away'),
               !condition %in% c('random_locations','no_schema')) %>%
        droplevels() %>%
        ggplot(aes(x=neighbor_status,
                   y=c_log,
                   fill=neighbor_status)) +
        geom_violin(alpha=0.5) +
        geom_boxplot(width=0.2,
                     alpha=0.2) +
        geom_point(alpha=0.2) +
        geom_line(aes(group=ptp_trunk),
                  alpha=0.2) +
        stat_summary(fun=mean, 
                     geom="point", 
                     shape=20, 
                     size=5, 
                     color="black",
                     fill="black") +         
        facet_grid(~accuracy_type+condition) +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
        ylab('Log C') +
        ggtitle('Log C')

```

Plot the difference values:

```{r learning-rates-difference-neighbor-island, fig.width=5, fig.height=4}

# Learning rates
sum_stats_each_participant %>%
        filter(neighbor_status != 'both',
               !condition %in% c('random_locations','no_schema'),
               accuracy_type %in% c('correct_one_square_away')) %>%
        droplevels() %>%
        pivot_wider(id_cols = c(ptp_trunk,
                                condition,
                                accuracy_type),
                    names_from = neighbor_status,
                    values_from = c) %>% 
        mutate(neighbor_diff = neighbor - island) %>% 
        ggplot(aes(x=condition,y=neighbor_diff)) +
        geom_violin() +
        # geom_jitter(width = 0.1, alpha = 0.2) +
        # geom_dotplot(binaxis='y', stackdir='center',
        #              stackratio=1, dotsize=0.3, fill="black",
        #              alpha=0.3) +       
        geom_point(alpha=0.3) +
        geom_line(aes(group=ptp_trunk,
                      color=ptp_trunk)) +
        stat_summary(fun=mean, geom="point", shape=20, size=5,
                     color="purple", fill="purple") +
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",size=1,width=0.1,color='purple') +
        facet_wrap(~accuracy_type, nrow = 1) +
        ylab('Diff') + 
        theme(legend.position = '') +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
        ggtitle('Landmark minus non-landmark, learning rate') +
        geom_hline(yintercept = 0, linetype = 'dashed')

# Learning rates
sum_stats_each_participant %>%
        filter(neighbor_status != 'both',
               !condition %in% c('random_locations','no_schema'),
               accuracy_type %in% c('correct_exact')) %>%
        droplevels() %>%
        pivot_wider(id_cols = c(ptp_trunk,
                                condition,
                                accuracy_type),
                    names_from = neighbor_status,
                    values_from = c) %>% 
        mutate(neighbor_diff = neighbor - island) %>% 
        ggplot(aes(x=condition,y=neighbor_diff)) +
        geom_violin() +
        # geom_jitter(width = 0.1, alpha = 0.2) +
        # geom_dotplot(binaxis='y', stackdir='center',
        #              stackratio=1, dotsize=0.3, fill="black",
        #              alpha=0.3) +       
        geom_point(alpha=0.3) +
        geom_line(aes(group=ptp_trunk,
                      color=ptp_trunk)) +
        stat_summary(fun=mean, geom="point", shape=20, size=5,
                     color="purple", fill="purple") +
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",size=1,width=0.1,color='purple') +
        facet_wrap(~accuracy_type, nrow = 1) +
        ylab('Diff') + 
        theme(legend.position = '') +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
        ggtitle('Landmark minus non-landmark, learning rate') +
        geom_hline(yintercept = 0, linetype = 'dashed')


# Now log C
# Learning rates
sum_stats_each_participant %>%
        filter(neighbor_status != 'both',
               !condition %in% c('random_locations','no_schema'),
               accuracy_type %in% c('correct_one_square_away')) %>%
        droplevels() %>%
        pivot_wider(id_cols = c(ptp_trunk,
                                condition,
                                accuracy_type),
                    names_from = neighbor_status,
                    values_from = c_log) %>% 
        mutate(neighbor_diff = neighbor - island) %>% 
        ggplot(aes(x=condition,y=neighbor_diff)) +
        geom_violin() +
        # geom_jitter(width = 0.1, alpha = 0.2) +
        # geom_dotplot(binaxis='y', stackdir='center',
        #              stackratio=1, dotsize=0.3, fill="black",
        #              alpha=0.3) +       
        geom_point(alpha=0.3) +
        geom_line(aes(group=ptp_trunk,
                      color=ptp_trunk)) +
        stat_summary(fun=mean, geom="point", shape=20, size=5,
                     color="purple", fill="purple") +
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",size=1,width=0.1,color='purple') +
        facet_wrap(~accuracy_type, nrow = 1) +
        ylab('Diff') + 
        theme(legend.position = '') +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
        ggtitle('Log C') +
        geom_hline(yintercept = 0, linetype = 'dashed')

# Learning rates
sum_stats_each_participant %>%
        filter(neighbor_status != 'both',
               !condition %in% c('random_locations','no_schema'),
               accuracy_type %in% c('correct_exact')) %>%
        droplevels() %>%
        pivot_wider(id_cols = c(ptp_trunk,
                                condition,
                                accuracy_type),
                    names_from = neighbor_status,
                    values_from = c_log) %>% 
        mutate(neighbor_diff = neighbor - island) %>% 
        ggplot(aes(x=condition,y=neighbor_diff)) +
        geom_violin() +
        # geom_jitter(width = 0.1, alpha = 0.2) +
        # geom_dotplot(binaxis='y', stackdir='center',
        #              stackratio=1, dotsize=0.3, fill="black",
        #              alpha=0.3) +       
        geom_point(alpha=0.3) +
        geom_line(aes(group=ptp_trunk,
                      color=ptp_trunk)) +
        stat_summary(fun=mean, geom="point", shape=20, size=5,
                     color="purple", fill="purple") +
        stat_summary(fun.data = mean_cl_normal,
                     geom = "errorbar",size=1,width=0.1,color='purple') +
        facet_wrap(~accuracy_type, nrow = 1) +
        ylab('Diff') + 
        theme(legend.position = '') +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
        ggtitle('Log C') +
        geom_hline(yintercept = 0, linetype = 'dashed')

```
